---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  results = "markup"
)
library(dirtyr, warn.conflicts = FALSE, verbose = FALSE)
```

# dirtyr

<!-- badges: start -->
<!-- badges: end -->

The goal of dirtyr is to provide additional tools for working with "dirty" data.
It is true that on second thought the name "dirtyr" doesn't sound as appropriate as possibly "cleanr".
In fact, I should probably change this because you may not want to put "dirtyr" into a search engine.

This package is in a very developmental state.
Use with caution.

## Installation

You can install the most recent development version of dirtyr from [GitHub](https://github.com/jmbarbone/dirtyr) with:

``` r
remotes::install_github("jmbarbone/dirtyr")
```

## Dates

Not every system will provide easily accessible dates.

```{r example date}
x <- c("UN Feb 2000", "1958", "17 UNK 1992")
unknown_date(x, format = "dmy")
unknown_date(x, format = "dmy", possible = "latest")
```

## Reindex

```{r example reindex}
x <- 2:5
names(x) <- letters[x]
new_index <- c(1, 3, 5, 7)
names(new_index) <- letters[new_index]
reindex(x, new_index = new_index)
```


## QC

```{r example qc}

```

## Smaller things

Easier conversions of non-numeric data to numeric (not just double).

```{r example as_numeric}
x <- c(as.character(1:5), NA, letters[1:2], "1e4")

## Throws an error
as.numeric(x)

## Doesn't throw an error
to_numeric(x)
maybe_numeric(x, names = TRUE)
```


```{r example as_numeric 2}
f <- factor(c(seq(0, 1, .2), "No", "Na_character_"))
## Uses factor level instead of text
suppressWarnings(as.numeric(f))
## uses text values instead
to_numeric(f)                    
maybe_numeric(f, names = TRUE)
```

